Ecuador plant species list

### 2022-09-12 code/L0/L0_1_Ecuador_plant_species_lists.Rmd
tidy up write csv to use output_path

## BIEN
```{r}
Ecuador_BIEN <- BIEN_occurrence_country("Ecuador")
write.csv(Ecuador_BIEN, "Ecuador_BIEN_species_list.csv")
```

@@

# Output data to csv
```{r}
write.csv(unique_species, "Ecuador_unique_species_list.csv")
```

>>>>

## BIEN
```{r}
Ecuador_BIEN <- BIEN_occurrence_country("Ecuador")
Ecuador_BIEN_species_list <- file.path(output_path,"Ecuador_BIEN_species_list.csv") 
write.csv(Ecuador_BIEN, file = Ecuador_BIEN_species_list)
```

@@

# Output data to csv
```{r}
Ecuador_unique_species_list <- file.path(output_path,"Ecuador_unique_species_list.csv") 
write.csv(unique_species, file = Ecuador_unique_species_list)
```
